Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-30 paper.tex
Add SI part to the anisotropy data
Add implications for exp

Although we have extensively shown that the treatment for the
dielectric nature differs in 2D (polarizability) and 3D (dielectric
constant) scenarios, a general picture of the dielectric properties in
both dimensions can still be drawn by studying the dielectric
anisotropy. The dielectric anisotropy index $\eta$ is defined as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange
square). The boundary separating the 2D and layered bulk materials is
determined using an linear support vector machine (SVM) classification
algorithm to be $y=0.048x+0.087$. The much lower $\eta$ values of 2D
materials compared with their bulk counterparts indicates a high
dielectric anisotropy, which is responsible for the unique 2D
optoelectronic properties, such as electrostatic transparency
\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
also observe that $\eta$ of 2D materials increase almost linearly with
$E_{\mathrm{g}}$, while such trend is absent for layered bulk
materials. The observations above can be explained by the principles
presented in thie work. As a result from the limited layer thickness
(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
$\eta$ of 2D materials. On the other hand, the fact that
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
layered bulk materials compared with the corresponding monolayer, and
making it possible to separate the 2D and layered bulk materials from
the $\eta-E_{\mathrm{g}}$ phase diagram. For comparison, we also
superimpose the dielectric anisotropy $\eta$ of common semiconducting
materials in other dimensions (details see Supplementary Section SXX
\todo{TBD}) on the phase diagram in Figure \ref{fig:aniso}. Bulk
covalent materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$)
show isotropic dielectric property, scattered on the line $\eta=1$. On
the other hand, reduced dimensionality increases the dielectric
anisotropy of materials such as planar organic semiconductor (OSc,
1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
e.g. polyacene). Interestingly, these materials also scatter along the
boundary line $y=0.048x+0.087$, indicating the criteria distinguishing
2D (more anisotropic) and bulk layered materials (more isotropic) from
the $\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
dimensions. From the phase diagram, we can see that 2D and bulk
layered materials (also including 2D van der Waals heterostructure
(vdWH) \cite{Novoselov_2016}), provides more flexibility in
controlling the dielectric and electronic properties, compared with semiconductors in other dimensions.

\todo{First leave this part untouched}
Finally, we would like to comment on the generality of the dielectric
nature between the 2D and 3D worlds. As schematically shown in Figure
\ref{fig-2D-3D}, the physical quantities related to the dielectric
properties can be categorized into (i) strictly 2D (microscopic), (ii)
strictly 3D (macroscopic) and (iii) valid both 2D and 3D.  $\alpha$
and $\varepsilon$ are the starting point for the strictly 2D and 3D
quantities, which require distinct definitions when dimensionality
changes. Such quantities include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (more
  details see Supplementary Section SXX \todo{TBD}).

\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
\end{enumerate}
These quantities have distinct units in both dimensions, and related
by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
plasma frequency), which requires prudent interpretation of
theoretical and experimental results. For instance, the experimentally
observed ``dielectric constant'' of monolayer 2D materials
\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
without considering the effect of mix ted medium. Instead, the 2D slab
polarizability, either transformed from the vacuum-containing
macroscopic dielectric constant, or predicted from the bandgap and
geometry as proposed here, will be a better descriptor for the true 2D
dielectric nature. On the other hand, there are also
dimension-independent quantities that valid for both 2D and 3D
systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
as well as the Hamaker constant of van der Waals interaction
$A_{\mathrm{H}}$. All these quantities are well-defined and can be
measured in both dimensions, while their relation with the dielectric
property varies with dimensionality. The well-known examples are the
different Wannier-Mott laws for exciton binding energy
\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
proposed here, and the distinct power laws for van der Waals
interactions \cite{Gobre_2013}. To get a accuracy description of
dielectric-related properties of the 2D materials and their
heterostructures, one has to distinguish between the 2D and 3D
properties, and choose a suitable relation with the
dimension-dependent and dimension-independent quantities.

\section{Conclusion}
\label{sec:org5fd1f1a}

To sum up, using first principles calculation for a large set of 2D
materials, we reveal the universal relation of the dielectric nature
of 2D materials using the 2D polarizability, as an analog to the Moss
relation for bulk semiconductors. The in-plane polarizability of a 2D
material is found to be inversely proportional to the minimal bandgap,
while the out-of-plane polarizability is the characteristic thickness
of the 2D material. Such universal scaling relation is explained by a
quantum mechanical model combining the polarizability in both
directions. Our universal scaling relation bridges the gap between 2D
and 3D dielectric properties with good accuracy of prediction.  Our
numerical findings and theoretical analysis pave the way to understand
and engineer the electronic and dielectric properties of a large
library of 2D materials for different technological applications in an
unified and unprecedented way.

>>>>

Although we have extensively shown that the treatment for the
dielectric nature differs in 2D (polarizability) and 3D (dielectric
constant) scenarios, a general picture of the dielectric properties in
both dimensions can still be drawn by studying the dielectric
anisotropy. The dielectric anisotropy index $\eta$ is defined as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange
square). The boundary separating the 2D and layered bulk materials is
determined using an linear support vector machine (SVM) classification
algorithm to be $y=0.048x+0.087$. The much lower $\eta$ values of 2D
materials compared with their bulk counterparts indicates a high
dielectric anisotropy, which is responsible for the unique 2D
optoelectronic properties, such as electrostatic transparency
\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
also observe that $\eta$ of 2D materials increase almost linearly with
$E_{\mathrm{g}}$, while such trend is absent for layered bulk
materials. The observations above can be explained by the principles
presented in thie work. As a result from the limited layer thickness
(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
$\eta$ of 2D materials. On the other hand, the fact that
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
layered bulk materials compared with the corresponding monolayer, and
making it possible to separate the 2D and layered bulk materials from
the $\eta-E_{\mathrm{g}}$ phase diagram. For comparison, we also
superimpose the dielectric anisotropy $\eta$ of common semiconducting
materials in other dimensions (details see Supplementary Section S4.5)
on the phase diagram in Figure \ref{fig:aniso}. Bulk covalent
materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$) show
isotropic dielectric property, scattered on the line $\eta=1$. On the
other hand, reduced dimensionality increases the dielectric anisotropy
of materials such as planar organic semiconductor (OSc, 1D-2D,
e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
e.g. polyacene). Interestingly, these materials also scatter along the
boundary line $y=0.048x+0.087$, indicating the criteria distinguishing
2D (more anisotropic) and bulk layered materials (more isotropic) from
the $\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
dimensions. From the phase diagram, we can see that 2D and bulk
layered materials (also including 2D van der Waals heterostructure
(vdWH) \cite{Novoselov_2016}), provides more flexibility in
controlling the dielectric and electronic properties, compared with
semiconductors in other dimensions.

\subsection{Implications for Experiments}
Finally, we would like to comment on the implications of this work for
the experiments concerning the dielectric properties of 2D materials.
As schematically shown in Figure \ref{fig-2D-3D}, the physical
quantities related to the dielectric properties can be categorized
into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
(iii) valid both 2D and 3D.  $\alpha$ and $\varepsilon$ are the
starting point for the strictly 2D and 3D quantities, which require
distinct definitions when dimensionality changes. Such quantities
include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

\item The plasma frequencies $\omega^{\mathrm{p}}_{\mathrm{2D}}$ and
  $\omega^{\mathrm{p}}_{\mathrm{2D}}$\cite{Nazarov_2015_2D_3D} (more
  details see Supplementary Section S4.4).

\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
\end{enumerate}
These quantities have distinct units in both dimensions, and related
by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
plasma frequency), which requires prudent interpretation of
theoretical and experimental results. For instance, the experimentally
observed ``dielectric constant'' of monolayer 2D materials
\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
without considering the effect of mix ted medium. Instead, the 2D slab
polarizability, either transformed from the vacuum-containing
macroscopic dielectric constant, or predicted from the bandgap and
geometry as proposed here, will be a better descriptor for the true 2D
dielectric nature. On the other hand, there are also
dimension-independent quantities that valid for both 2D and 3D
systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
as well as the Hamaker constant of van der Waals interaction
$A_{\mathrm{H}}$. All these quantities are well-defined and can be
measured in both dimensions, while their relation with the dielectric
property varies with dimensionality. The well-known examples are the
different Wannier-Mott laws for exciton binding energy
\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
proposed here, and the distinct power laws for van der Waals
interactions \cite{Gobre_2013}. To get a accuracy description of
dielectric-related properties of the 2D materials and their
heterostructures, one has to distinguish between the 2D and 3D
properties, and choose a suitable relation with the
dimension-dependent and dimension-independent quantities.
\todo[inline]{I plan to use the original section for the ``implication for experiments''. Please help to add more on this part.}

\section{Conclusion}
\label{sec:org5fd1f1a}
\todo[inline]{To be changed later when everything fixed}
To sum up, using first principles calculation for a large set of 2D
materials, we reveal the universal relation of the dielectric nature
of 2D materials using the 2D polarizability, as an analog to the Moss
relation for bulk semiconductors. The in-plane polarizability of a 2D
material is found to be inversely proportional to the minimal bandgap,
while the out-of-plane polarizability is the characteristic thickness
of the 2D material. Such universal scaling relation is explained by a
quantum mechanical model combining the polarizability in both
directions. Our universal scaling relation bridges the gap between 2D
and 3D dielectric properties with good accuracy of prediction.  Our
numerical findings and theoretical analysis pave the way to understand
and engineer the electronic and dielectric properties of a large
library of 2D materials for different technological applications in an
unified and unprecedented way.
